Stuff that may well go into the project report

### 2014-09-23 stuff_somewhat_organised.tex
Skrevet enda litt mer.

\theoremstyle{remark}
\newtheorem{obs}{Observation}
\newtheorem{rem}{Remark}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		ENERGY SOLUTIONS:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Energy solutions}
We define  $\Psi$ as the primitive of $\Phi$ with $\Psi(0) = 0$, i.e.
\begin{equation*}
	\Psi(s) = \int_0^s \Phi(u) ds.
\end{equation*}
With this in mind we can define energy solutions in the following way:
\begin{mydef}[Energy solution]
We say that $u$ is a \textbf{weak energy solution} if it's a weak solution, and $u_0 \in L^1(\Omega)$ and $\Psi(u_0) \in L^1(\Omega)$, and the energy inequality
\begin{equation}
\label{energy_ineq}
\iint_{Q_T} |\nabla \Phi(u)|^2 dxdt + \int_\Omega \Psi(u(x,T))dx \leq \int_\Omega \Psi(u_0)dx + \iint_{Q_T}f\Phi(u)dxdt
\end{equation}
holds.
\end{mydef}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%					ESTIMATES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Some estimates}
Now we need to make some assumptions on $\Phi$ and $f$:
\begin{enumerate}[i)]
	\item The function $\Phi: \mathbb{R} \to \mathbb{R}$ is continuous, strictly increasing and we assume $\Phi(0) = 0$ without any loss of generality.
\end{enumerate}

@@

	\item For the second integral it is helpful to first only consider integration of the temporal dimensions, leaving us with
	\begin{align*}
	&\int_0^T\int_t^T \nabla(\Phi(u_2(t)) - \Phi(u_1(t)))\cdot \nabla(\Phi(u_2(s))-\Phi(u_1(s)))dsdt \\
	&= \int_0^T\int_0^s\nabla(\Phi(u_2(t)) - \Phi(u_1(t)))\cdot \nabla(\Phi(u_2(s))-\Phi(u_1(s)))dtds.
	\end{align*}
	Due to the symmetry about the line $s=t$, we have
	\begin{align*}
	&\int_0^T\int_0^s\nabla(\Phi(u_2(t)) - \Phi(u_1(t)))\cdot \nabla(\Phi(u_2(s))-\Phi(u_1(s)))dtds \\
	&= \frac{1}{2}\int_0^T \int_0^T \nabla(\Phi(u_2(t)) - \Phi(u_1(t)))\cdot \nabla(\Phi(u_2(s))-\Phi(u_1(s)))dtds \\
	&= \frac{1}{2}\left( \int_0^T \nabla(\Phi(u_2)-\Phi(u_1))dt\right)^2,
	\end{align*}
	which is also nonnegative, and therefore the second integral in (\ref{unique}) must also be nonnegative.
\end{enumerate}
From this we may conclude that both integral terms in (\ref{unique}) are zero, which in turn implies, by the first integral that $(\Phi(u_2)-\Phi(u_1))(u_2 - u_1) = 0$ a.e. in $Q_T$. Actually, we have that $\Phi(u_2) - \Phi(u_1) = 0$ a.e., because wherever $u_2 = u_1$ it is trivially true, and wherever $ u_2 \neq u_1$ it holds from the first integral being zero. Thus, $ \nabla (\Phi(u_2) - \Phi(u_1) ) = 0$ a.e. and putting this into (\ref{weak_diff}) we get that
\begin{equation*}
\iint_{Q_T}(u_2 - u_1)\partial_t \eta dx dt = 0.
\end{equation*}
This should hold for any test function $\eta$, and so the weak derivative of $u_2 - u_1$ with respect to time is zero. Because $u_2$ and $u_1$ have identical initial condition $u_0$ we conclude that $u_2 = u_1$.
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%				APPENDICES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{appendices}
\section{Passing derivative inside the integral}
\label{sec:derivative}

>>>>

%\theoremstyle{plain}
\newtheorem{obs}{Observation}
\newtheorem{rem}{Remark}

@@

\begin{obs}
With $u_0 \in L^1(\Omega)$ and $f\in L^1(Q_T)$, all the integrals in (\ref{weak}) make sense.
\end{obs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		ENERGY SOLUTIONS:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Energy solutions}
We define  $\Psi$ as the primitive of $\Phi$ with $\Psi(0) = 0$, i.e.
\begin{equation*}
	\Psi(s) = \int_0^s \Phi(u) ds.
\end{equation*}
With this in mind we can define energy solutions in the following way:
\begin{mydef}[Energy solution]
We say that $u$ is a \textbf{weak energy solution} if it's a weak solution, and $u_0 \in L^1(\Omega)$ and $\Psi(u_0) \in L^1(\Omega)$, and the energy inequality
\begin{equation}
\label{energy_ineq}
\iint_{Q_T} |\nabla \Phi(u)|^2 dxdt + \int_\Omega \Psi(u(x,T))dx \leq \int_\Omega \Psi(u_0)dx + \iint_{Q_T}f\Phi(u)dxdt
\end{equation}
holds.
\end{mydef}

\subsubsection{Derivation of energy estimate for classical solutions}
Suppose $u$ is a smooth solution of (\ref{HDP}). We proceed by multiplying the equation with $\Phi(u)$ to get
\begin{equation*}
\Phi(u)\partial_t u = \Phi(u)\Delta \Phi(u) + \Phi(u)f,
\end{equation*}
and we notice that $\Phi(u)\partial_t u = \partial_t \Psi(u)$. That means when we integrate over $Q_T$ we have
\begin{equation*}
\iint_{Q_T} \partial_t \Psi(u)dxdt = \int_\Omega \Psi(u(T))dx - \int_\Omega \Psi(u_0)dx.
\end{equation*}
On the diffusive term we can use integration by parts, so
\begin{equation*}
\iint_{Q_T}\Phi(u) \Delta \Phi(u) dxdt = -\iint_{Q_T} |\nabla \Phi(u)|^2dxdt + \int_0^T \int_{\partial\Omega} \Phi(u)\nabla \Phi(u) \cdot \hat{n}dS,
\end{equation*}
where $\hat{n}$ is the outward unit normal. By the Dirichlet condition
\begin{equation*}
\iint_{Q_T}\Phi(u) \Delta \Phi(u) dxdt = -\iint_{Q_T} |\nabla \Phi(u)|^2dxdt,
\end{equation*}
and notice that this step would have been valid for homogeneous Neumann condition as well. In toto 
\begin{equation}
\iint_{Q_T} |\nabla \Phi(u)|^2dxdt + \int_\Omega \Psi(u(T))dx = \int_\Omega \Psi(u_0)dx + \iint_{Q_T} f\Phi(u)dxdt.
\end{equation}

\setcounter{obs}{0}
\begin{obs}
In contrast to (\ref{energy_ineq}) we have equality for smooth solutions.
\end{obs}

\begin{obs}
We can go even further and deal with the last term on the right hand side: Assuming $f,\Phi(u) \in L^2(Q_T)$, then
\begin{equation*}
\iint_{Q_T} f\Phi(u)dxdt \leq \left(\iint_{Q_T} f^2 dxdt\right)^\frac{1}{2}\left(\iint_{Q_T} \Phi(u)^2 dxdt\right)^\frac{1}{2},
\end{equation*}
by Cauchy-Schwarz'. With the inequality $\sqrt{ab} \leq \frac{1}{4c}a + cb$ for $c>0$
\begin{equation*}
\iint_{Q_T} f\Phi(u)dxdt \leq \frac{1}{4c}\iint_{Q_T}f^2dxdt + c\iint_{Q_T}\Phi(u)^2dxdt.
\end{equation*}
Lastly, because of the homogeneous Dirichlet conditions, we use the Poincaré inequality and set $c$ so that
\begin{equation*}
\iint_{Q_T} f\Phi(u)dxdt \leq C\iint_{Q_T}f^2dxdt + \frac{1}{2}\iint_{Q_T}|\nabla \Phi(u)|^2dxdt,
\end{equation*}
and the final inequality becomes
\begin{equation}
\frac{1}{2}\iint_{Q_T}|\nabla \Phi(u)|^2dxdt + \int_\Omega \Psi(u(T))dx \leq \int_\Omega \Psi(u_0)dx + C\iint_{Q_T}f^2dxdt.
\end{equation}
\end{obs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%					ESTIMATES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Some estimates}
Now we need to make some assumptions on $\Phi$ and $f$:
\begin{enumerate}[i)]
	\item The function $\Phi: \mathbb{R} \to \mathbb{R}$ is continuous, strictly increasing and we assume $\Phi(0) = 0$ without any loss of generality.
\end{enumerate}

@@

	\item For the second integral it is helpful to first only consider integration of the temporal dimensions, leaving us with
	\begin{align*}
	&\int_0^T\int_t^T \nabla(\Phi(u_2(t)) - \Phi(u_1(t)))\cdot \nabla(\Phi(u_2(s))-\Phi(u_1(s)))dsdt \\
	&= \int_0^T\int_0^s\nabla(\Phi(u_2(t)) - \Phi(u_1(t)))\cdot \nabla(\Phi(u_2(s))-\Phi(u_1(s)))dtds.
	\end{align*}
	Due to the symmetry about the line $s=t$, we have
	\begin{align*}
	&\int_0^T\int_0^s\nabla(\Phi(u_2(t)) - \Phi(u_1(t)))\cdot \nabla(\Phi(u_2(s))-\Phi(u_1(s)))dtds \\
	&= \frac{1}{2}\int_0^T \int_0^T \nabla(\Phi(u_2(t)) - \Phi(u_1(t)))\cdot \nabla(\Phi(u_2(s))-\Phi(u_1(s)))dtds \\
	&= \frac{1}{2}\left( \int_0^T \nabla(\Phi(u_2)-\Phi(u_1))dt\right)^2,
	\end{align*}
	which is also nonnegative, and therefore the second integral in (\ref{unique}) must also be nonnegative.
\end{enumerate}
From this we may conclude that both integral terms in (\ref{unique}) are zero, which in turn implies, by the first integral that $(\Phi(u_2)-\Phi(u_1))(u_2 - u_1) = 0$ a.e. in $Q_T$. Actually, we have that $\Phi(u_2) - \Phi(u_1) = 0$ a.e., because wherever $u_2 = u_1$ it is trivially true, and wherever $ u_2 \neq u_1$ it holds from the first integral being zero. Thus, $ \nabla (\Phi(u_2) - \Phi(u_1) ) = 0$ a.e. and putting this into (\ref{weak_diff}) we get that
\begin{equation*}
\iint_{Q_T}(u_2 - u_1)\partial_t \eta dx dt = 0.
\end{equation*}
This should hold for any test function $\eta$, and so the weak derivative of $u_2 - u_1$ with respect to time is zero. Because $u_2$ and $u_1$ have identical initial condition $u_0$ we conclude that $u_2 = u_1$.
\end{proof}

\setcounter{obs}{0}
\begin{obs}
Provided $\iint_{Q_T} f\Phi(u)dxdt$ in (\ref{energy_ineq}) makes sense, $\Phi(u) \in L^2(0,T: H_0^1(\Omega))$ for weak energy solutions. If we can put on a condition on $u$ or any of the data to ensure that $u \in L^2(Q_T)$, we would have a condition under which weak energy solutions are unique. Hopefully, no such condition is required, but will perhaps follow from some other estimate.
\end{obs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%				APPENDICES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{appendices}
\section{Passing derivative inside the integral}
\label{sec:derivative}
